---
output: github_document
bibliography: README-references.bib
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# outselect

The goal of outselect (outlier detection method selection) is to select  suitable outlier detection methods for a given dataset using meta-features. The functionality is available to reproduce some instance space results in our papers [@normalizationoutliers] and [@outliersinstance].   

This package is still under development and this repository contains a development version of the R package  *outselect*.


## Installation

You can install  outselect from github with:

``` r
#install.packages("devtools")
devtools::install_github("sevvandi/outselect")
```

## Example 1
This example shows how to compute the meta-features and predict which outlier method is good for this dataset. For this example we use a dataset described in [@campos2016evaluation]

```{r example1, cache=TRUE}
library(outselect)
data(Arrhythmia_withoutdupl_05_v05)
dat <- Arrhythmia_withoutdupl_05_v05
feat <- ComputeMetaFeaturesMM(dat)
fit <- TrainModels(1,1,1)
out <- PredictPerformance(feat, fit)
out
```

## Example 2
This example shows how to plot the instance *Arrhythmia_withoutdupl_05_v05* on the instance space.

```{r example2, cache=TRUE}
library(outselect)
data(Arrhythmia_withoutdupl_05_v05)
dat <- Arrhythmia_withoutdupl_05_v05
feat <- ComputeMetaFeaturesMM(dat)
svmout <- DrawInstSpace(d=1)
PlotNewInstance(svmout, feat)
```



## References
