---
output: github_document
bibliography: README-references.bib
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# outselect 


[![Travis build status](https://travis-ci.org/sevvandi/outselect.svg?branch=master)](https://travis-ci.org/sevvandi/outselect)

The goal of outselect (outlier detection method selection) is to select  suitable outlier detection methods for a given dataset using meta-features. The functionality is available to reproduce some instance space results in our papers [@normalizationoutliers] and [@outliersinstance].   

This package is still under development and this repository contains a development version of the R package  *outselect*.


## Installation

You can install  outselect from github with:

``` r
#install.packages("devtools")
devtools::install_github("sevvandi/outselect")
```

## Features
Details on features can be found [here.](./Features.md)


## Min-Max Normalization
These examples are related to the work in [@outliersinstance] and use Min-Max normalization and the outlier detection methods described in [@campos2016evaluation]. For all examples we use the dataset *Arrhythmia_withoutdupl_05_v05*, which is described in [@campos2016evaluation].

### Example 1
This example shows how to compute the meta-features and predict which outlier method is good for the dataset *Arrhythmia_withoutdupl_05_v05*.

```{r example1}
library(outselect)
data(Arrhythmia_withoutdupl_05_v05)
dat <- Arrhythmia_withoutdupl_05_v05
feat <- ComputeMetaFeaturesMM(dat)
fit <- TrainModels(1,1,1)
out <- PredictPerformance(feat, fit)
out
```

### Example 2
This example shows how to plot the instance *Arrhythmia_withoutdupl_05_v05* on the Min-Max instance space.

```{r example2}
library(outselect)
data(Arrhythmia_withoutdupl_05_v05)
dat <- Arrhythmia_withoutdupl_05_v05
feat <- ComputeMetaFeaturesMM(dat)
svmout <- InstSpace(d=1)
PlotNewInstance(svmout, feat, vis=TRUE)
```

## Min-Max and Median-IQR normalization methods
These examples are related to the work in [@normalizationoutliers]. We use Min-Max and Median-IQR normalization methods for feature computation. For the instance space we use the following normalization and  outlier detection method  combinations:

1. Ensemble Median-IQR
2. LOF Min-Max
3. KNN Median-IQR
4. FAST ABOD Min-Max
5. iForest Median-IQR
6. KDEOS Median-IQR
7. KDEOS Min-Max and
8. LDF Min-Max

Again, for all examples we use the dataset *Arrhythmia_withoutdupl_05_v05*, which is described in [@campos2016evaluation].

### Example 3
This example shows how to compute the meta-features and predict which outlier-normalization combination is good for the dataset *Arrhythmia_withoutdupl_05_v05*.

```{r example3}
library(outselect)
data(Arrhythmia_withoutdupl_05_v05)
dat <- Arrhythmia_withoutdupl_05_v05
feat <- ComputeMetaFeaturesAll(dat)
fit <- TrainModels(d=2,1,1)
out <- PredictPerformance(feat, fit)
out
```

### Example 4
This example plots the same instance in the outlier-normalization algorithm instance space.
```{r example4}
library(outselect)
data(Arrhythmia_withoutdupl_05_v05)
dat <- Arrhythmia_withoutdupl_05_v05
feat <- ComputeMetaFeaturesAll(dat)
svmout <- InstSpace(d=2)
PlotNewInstance(svmout, feat, vis=TRUE)
```


## References
